---
title: "RWorksheet_Lapso4b.rmd"
author: "Darlene Erl Lapso"
date: "`r Sys.Date()`"
output: pdf_document
---

---
title: "RWorksheet_Lapso#4b.Rmd"
author: "DARLENE ERL LAPSO"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r 1}
vectorA <- c(1,2,3,4,5)
matzero_A <- matrix(0, nrow = 5, ncol = 5)

mat_A <- matzero_A
for(i in 1:5) {
  for (j in 1:5) {
  mat_A[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}

print(mat_A)
```


``` {r 2}
n <- 5
for (i in 1:n) {
  for (i in 1:i) {
    cat("* ")
  }
  cat("\n")
}
```

```{r 3}
pos_int <- function(prompt) {
  repeat {
    input <- as.integer(readline(prompt))
    if (!is.na(input) && input > 0) {
      return(input)
    } else {
      cat("Please enter a valid positive integer.\n")
    }
  }
}

n <- pos_int("Enter the starting number for the Fibonacci sequence: ")

a <- 0
b <- 1
 cat("Fibonacci sequence starting from", n, "and up to 500:\n")
repeat {
  if (a >= n) {
    cat(a, " ")
  }
  c <- a + b
  a <- b
  b <- c
  if (a > 500) {
    break
  }
}
```

```{r 4}
install.packages("readxl")
library(readxl)
shoe <- read_excel("SHOE.xlsx")
shoe

head(shoe, 6)
maleSub <- subset(shoe, Gender...3  == "M")
femaleSub <- subset(shoe, Gender...3  == "F")

Male <- nrow(maleSubset)
Female <- nrow(femaleSubset)

cat("Number of observations of Male in Gender...3 is: ", Male, "\n")
cat("Number of observations of Female in Gender...3 is: ", Female, "\n")
```


```{r 5}
DelaCruz <- c(60, 10, 5, 25)
  pie(DelaCruz, 
      main = "Dela Cruz's Monthly Income",
      col = rainbow(length(DelaCruz)),
      labels = c("Food", "Electricity", "Savings", "Miscellaneous"))
```


```{r 6a}
data(iris)
iris
View(iris)
str(iris)
```

```{r 6b}
sl <- mean(iris$Sepal.Length)
sw <- mean(iris$Sepal.Width)
pl <- mean(iris$Petal.Length)
pw <- mean(iris$Petal.Width)

sl
sw
pl
pw
```

```{r 6c}
pie(table(iris$Species), main = "Species Distribution", col = rainbow(3), labels = levels(iris$Species))
```

```{r 6d}
setosaSub <- tail(subset(iris, Species == "setosa"), 6)
versicolorSub <- tail(subset(iris, Species == "versicolor"), 6)
virginicaSub <- tail(subset(iris, Species == "virginica"), 6)
setosaSub
versicolorSub
virginicaSub
```

```{r 6e}
iris$Species<- as.factor(iris$Species)
plot(iris$Sepal.Length,iris$Sepal.Width,pch = as.integer(iris$Species),col = as.integer(iris$Species), main = "Iris Dataset", sub = "Sepal Width and Length", xlab = "Sepal Length", ylab = "Sepal width")
```

the provided code successfully creates subsets for the Male and Female categories in the data set. Additionally, it demonstrates how to use R to analyze the data and interpret the results. The findings suggest that the data set may have more data on male individuals than female individuals and that the iris species can be distinguished by the length and width of their sepal and petal attributes.


```{r 7}
install.packages("readxl")
library(readxl)
alexa <- read_excel("alexa_file.xlsx")
print(alexa)

alexa$variation <- gsub(" Black", "Blue", alexa$variation)
alexa$variation <- gsub(" White", "Yellow", alexa$variation)

View(alexa)
```

```{r 7snip}
knitr::include_graphics("alexa_file.xlsx")
```

```{r 7b}
library(readxl)
library(dplyr)

original_data <- read.xlsx("alexa_file.xlsx")

variations <- original_data %>%
  count(original_data$variation)

save(variations, file = "variations.RData")
```

```{r 7c}
# Load the necessary libraries
install.packages("ggplot2")
library(ggplot2)

# Load the data from the renamed RData file
load("variations.RData")

x <- c("Black", "Black Plus", "Black Show", "Black Spot", "Black Dot")
y <- c(0, 100, 200, 400, 500)

#barplot(y, x, main = "Black Variants", xlab = NULL, ylab = "Variants", col = c("#000000", "#ff69b4", "#32cd32", "#87ceeb", "#43a047"))




```











