---
title: "RWorksheet_Lapso4c.Rmd"
author: "Darlene Erl Lapso"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

---
title: "RWorksheet_Lapso4c.Rmd"
author: "Darlene Erl Lapso"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

a.  Show your solutions on how to import a csv file into the
    environment.

```{r}
library(csv)

data(mpg)

getwd()
setwd("C:/Users/steve/Documents/lapso-worksheetactivity/worksheet#4")
mpg <- read.csv("D:/darlene/CS101/mpg.csv")
head(mpg)

```

b.  Which variables from mpg dataset are categorical?

```{r}
library(ggplot2)
data(mpg)
str(mpg)
```

#1b. 'manufacturer' shows different kinds of vehicle manufacturer,
'model' shows different model of a vehicles 'drv' shows different types
of drive (e.g., front-wheel drive, rear-wheel drive) 'fl' shows fuel
types used by vehicles.

c.  Which are continuous variables? #1c in the mpg dataset, the
    continuous variables are those shown as numbers (like engine
    displacement in liters for 'displ'). Additionally, there are other
    number-based variables like 'hwy' and 'cty' (representing miles per
    gallon on the highway and in the city), along with 'year'. However,
    these numeric variables might not be purely continuous; some, like
    'year', could represent categories or ordered values rather than a
    smooth range of numbers.

---------------

2.1 Which manufacturer has the most models in this data set? Which model
has the most variations? Show your answer

```{r}
mostManu <- names(sort(table(mpg$manufacturer), decreasing = TRUE))[1]
mostVar <- names(sort(table(mpg$model), decreasing = TRUE))[1]
```

```{r}
mostManu
```

```{r}
mostVar
```

a.  Group the manufacturers and find the unique models. Show your codes
    and result

```{r}
library(dplyr)
uniqueModMan <- mpg %>%
  group_by(manufacturer) %>%
  summarize(unique_models = n_distinct(model))
uniqueModMan
```

b.  Graph the result by using plot() and ggplot(). Write the codes and
    its result

```{r}
library(ggplot2)
ggplot(uniqueModMan, aes(x = manufacturer, y = unique_models)) +
  geom_bar(stat = "identity", fill = "beige", color = "black") +
  labs(x = "Manufacturer", y = "Unique Models",
       title = "Unique Models by Manufacturer using ggplot") +
  theme_minimal()
```

2.2 a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point()
show?

```{r}
library(ggplot2)
pointsMPG <- ggplot(mpg, aes(model, manufacturer)) +
  geom_point() +
  labs(x = "Model", y = "Manufacturer",
       title = "Relationship between Model and Manufacturer")
pointsMPG
```

This plot could display how car models are spread out among various
manufacturers or how particular models are distributed across different
manufacturers. Yet, due to potential overlapping points or the
categorical nature of the variables, it might not offer a clear or
meaningful representation of the direct relationship between the model
and the manufacturer.

b.  For you, is it useful? If not, how could you modify the data to make
    it more informative?

I think the plot isn't very helpful because it might have overlapping
points, making it hard to see how car models relate to manufacturers.

What I could do to do it more is to group/combine data or use a
different geom graph.

------------------------------------------------------------------------

3.  Plot the model and the year using ggplot(). Use only the top 20
    observations. Write the codes and its results.

```{r}
library(ggplot2)
top_20 <- head(mpg, 20)
ggplot(top_20, aes(x = year, y = model)) +
  geom_point() +
  labs(x = "Year", y = "Model", title = "Top 20 Observations: Model vs Year")
```

------------------------------------------------------------------------

4.  Using the pipe (%\>%), group the model and get the number of cars
    per model. Show codes and its result

```{r}
library(dplyr)

cars_per_model <- mpg %>%
  group_by(model) %>%
  summarize(num_cars = n())

cars_per_model
```

a.  Plot using geom_bar() using the top 20 observations only. The graphs
    should have a title, labels and colors. Show code and results.

```{r}
library(ggplot2)

model_counts <- mpg %>%
  group_by(model) %>%
  summarise(Num_Cars = n()) %>%
  top_n(20, Num_Cars)


ggplot(model_counts, aes(x = Num_Cars, y = reorder(model, Num_Cars), fill = model)) +
 geom_bar(stat = "identity") +
 scale_fill_manual(values = rainbow(nrow(model_counts))) +
 labs(x = "Number of Cars", y = "Model", title = "Number of Cars per Model (Top 20)") +
 theme(axis.text.y = element_text(angle = 0))
```

b.  Plot using the geom_bar() + coord_flip() just like what is shown
    below. Show codes and its result.

```{r}
top_20 <- head(mpg, 20)
ggplot(top_20, aes(x = model, fill = model)) +
  geom_bar() +
  labs(x = "Count", y = "Model", fill = "Model",
       title = "Top 20 Car Models Count (Horizontal)") +
  coord_flip() + 
  theme(axis.text.y = element_text(hjust = 1)) + 
  scale_fill_brewer(palette = "Set3")
```

5.  Plot the relationship between cyl - number of cylinders and displ -
    engine displacement using geom_point with aesthetic color = engine
    displacement. Title should be "Relationship between No. of Cylinders
    and Engine Displacement".

```{r}
ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(x = "Number of Cylinders", y = "Engine Displacement",
       title = "Relationship between No. of Cylinders and Engine Displacement") +
  scale_color_continuous(name = "Engine Displacement")
```
a. How would you describe its relationship? Show the codes and its result.

When working with categorical variables like 'model' and 'year', a bar
plot might not effectively illustrate their direct relationship.
However, by displaying the counts for each unique pairing of 'model' and
'year', we can identify patterns or frequencies within this constrained
data set. 

------

6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). 
Mapped it with a continuous variable you have identified in #1-c. 
What is its result? Why it produced such output?

```{r}
library(ggplot2)
data(mpg)

mpg$year <- as.factor(mpg$year)

ggplot(mpg, aes(x = displ, y = hwy, color = year)) +
  geom_point() +
  labs(x = "Engine Displacement", y = "Highway MPG",
       title = "Relationship between Displacement and Highway MPG\nMapped with Year") +
  scale_color_brewer(palette = "RdYlBu")
```

-------

6. Import the traffic.csv onto your R environment.
```{r}
library(readr)
getwd
setwd("C:/Users/steve/Documents/lapso-worksheetactivity/worksheet#4")
traffic <- read.csv("D:/darlene/CS101/traffic.csv", header = TRUE, sep = ",")
traffic
```

a. How many numbers of observation does it have? What are the variables of the traffic dataset the Show
your answer.
```{r}
dim(traffic)
str(traffic)
```

b. subset the traffic dataset into junctions. What is the R codes and its output?
```{r}
Junc_subset=subset(traffic, Junction < 10)
Junc_subset
```

```{r}
library(ggplot2)
ggplot(Junc_subset, aes(x = Junction, y = Vehicles, group = Junction, color = Junction)) +
  geom_line() +
  labs(x = "Junction", y = "Vehicle", title = "Traffic Flow at Different Junctions") +
  theme_minimal()
```

7. From alexa_file.xlsx, import it to your environment
```{r}
library(readxl)
alexa <- read_excel("alexa_file.xlsx")

```

a. How many observations does alexa_file has? What about the number of columns? Show your solution
and answer.
```{r}
dim(alexa)
str(alexa)
```

b. group the variations and get the total of each variations. Use dplyr package. Show solution and
answer.

```{r}
library(dplyr)

alexaVar <- alexa %>%
  group_by(variation) %>%
  summarise(Total_Count = n())

alexaVar
```

c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the
graph. Show solution and answer.

```{r}
library(ggplot2)
ggplot(alexa, aes(x = variation)) +
  geom_bar(fill = "red") +
  labs(x = "Variations", y = "Frequency", title = "Frequency of Variations in Alexa Dataset") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the
graphs. Show your answer and solution.
```{r}
library(ggplot2)
library(dplyr)

review_counts <- alexa %>%
  group_by(date) %>%
  summarise(Num_Reviews = n())

ggplot(review_counts, aes(x = date, y = Num_Reviews, group = 1)) +
  geom_line(color = "blue") +
  labs(x = "Date", y = "Number of Verified Reviews", title = "Verified Reviews Over Time") +
  theme_minimal()
```


e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a
graph to show its relationship. Show your solution and answer.
```{r}
library(dplyr)
library(ggplot2)

variation_ratings <- alexa %>%
  group_by(variation) %>%
  summarise(Avg_Rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(Avg_Rating))

variation_ratings$variation[which.max(variation_ratings$Avg_Rating)]

ggplot(variation_ratings, aes(x = reorder(variation, Avg_Rating), y = Avg_Rating)) +
  geom_bar(stat = "identity", fill = "gold") +
  labs(x = "Variations", y = "Average Rating", title = "Relationship of Variations and Ratings") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



















