---
title: "RWorksheet_5.rmd"
author: "Darlene Erl Lapso"
date: "`r Sys.Date()`"
output: html_document
---

---


1. Create a data frame for the table below. Show your solution.
a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
```{r}
library(Hmisc)
library(pastecs)
studentData<- data.frame(
  Student <- c(1:10),
  preTest <- c(55,54,47,57,51,61,57,54,63,58),
  postTest <- c(61,60,56,63,56,63,59,56,62,61))

colnames(studentData) <- c("Student", "Pre-Test","Post-Test")
studentData
```

2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r}
fertLevels <- c(10,10,10, 20,20,50,10,20,10,50,20,50,20,10.)
ordered(fertLevels)
```

3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense.
```{r}
exLevels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")
factor_exLevels<- factor(exLevels)
levels(factor_exLevels) <- c("none","light","intense")
factor_exLevels
```

4a.a. Apply the factor function and factor level. Describe the results.
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
"vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
"wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
"vic", "vic", "act")
statef<-factor(state)
levels(statef) 
statef
```

5. From #4 - continuation:
• Suppose we have the incomes of the same tax accountants in another vector (in suitably large units of money).
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

incmeans <- tapply(incomes, statef, mean)
incmeans

data <- data.frame(State = statef, Income = incomes)
data
```
b. Copy the results and interpret
     act      nsw       nt      qld       sa      tas 
44.50000 57.33333 55.50000 53.60000 55.00000 60.50000 
     vic       wa 
56.00000 52.25000 

This result shows the average income of the different/individual states in Australia

------------------

6.Calculate the standard errors of the state income means (refer again to number 3)

```{r}
stdError <- function(x) sqrt(var(x) / length(x))
incster <- tapply(incomes, statef, stdError)

incster
```
 b, Interpret the result
 
 The standard error of the state incomes mean of different states, 
 
 
 
 
 
 